Visualizations for the manuscript

### 2022-05-13 metanalysis_visualization/manuscript_Figures.Rmd
before after slope significance test implementations + reformating + CI table1 fixing

Put all the aggregated counts from the different sites together
```{r}
for( i in 1:length( outputFiles )){
  print(outputFiles[i])
  load(paste0( outputDir, outputFiles[i]))
  if( i == 1 ){
    count_icd_all <- count_icd
    patients_hospitalized_agg_sex_perc_all <- patients_hospitalized_agg_sex_perc
    patient_count_psy_period_psy_all <- patient_count_psy_period_psy
    perc_disorder_group_all <- perc_disorder_group
    ratios_patients_with_without_psy_all <- ratios_patients_with_without_psy
    bootstrapped_fitted_all <- bootstrapped_fitted_df
    bootstrapped_coefficients_all <- bootstrapped_coefficients_df
    length_hospitalisation_values_all <- length_hospitalisation_values
    mental_codes_qc_output_all <- mental_codes_qc_output %>%
      select( disorder_group, description, concept_code, distinct_patients, distinct_observations, siteid )
    table1_all <- table1
  } else {
    count_icd_all <- rbind(count_icd_all, count_icd)
    perc_disorder_group_all <- rbind(perc_disorder_group_all, perc_disorder_group)
    patients_hospitalized_agg_sex_perc_all <- rbind( patients_hospitalized_agg_sex_perc_all, patients_hospitalized_agg_sex_perc)
    mental_codes_qc_output_all <- rbind( mental_codes_qc_output_all,
                                         mental_codes_qc_output %>%
                                           select( disorder_group, description, concept_code, distinct_patients, distinct_observations, siteid )
    )
    table1_all <- rbind( table1_all, table1)
    patient_count_psy_period_psy_all <- rbind( patient_count_psy_period_psy_all,patient_count_psy_period_psy)
    ratios_patients_with_without_psy_all <- rbind( ratios_patients_with_without_psy_all, ratios_patients_with_without_psy)
    bootstrapped_fitted_all <- rbind(bootstrapped_fitted_all, bootstrapped_fitted_df)
    bootstrapped_coefficients_all <- rbind(bootstrapped_coefficients_all, bootstrapped_coefficients_df)
    length_hospitalisation_values_all <- tryCatch(
      rbind(length_hospitalisation_values_all, length_hospitalisation_values),
      error = function(e) length_hospitalisation_values_all
    )
    rm(count_icd,patients_hospitalized_agg_sex_perc,patient_count_psy_period_psy,
       perc_disorder_group,ratios_patients_with_without_psy,
       patient_count_psy_period_psy_clear, bootstrapped_coefficients_df,
       bootstrapped_fitted_df, mental_codes_qc_output, table1, length_hospitalisation_values)
  }
}

@@

bootstrapped_fitted_all <- filter_by_dates(bootstrapped_fitted_all, start_date_plots, end_date_plots)
count_icd_all <- filter_by_dates(count_icd_all, start_date_plots, end_date_plots)
patient_count_psy_period_psy_all <- filter_by_dates(patient_count_psy_period_psy_all, start_date_plots, end_date_plots)
patients_hospitalized_agg_sex_perc_all <- filter_by_dates(patients_hospitalized_agg_sex_perc_all, start_date_plots, end_date_plots)
perc_disorder_group_all <- filter_by_dates(perc_disorder_group_all, start_date_plots, end_date_plots)
ratios_patients_with_without_psy_all <- filter_by_dates(ratios_patients_with_without_psy_all, start_date_plots, end_date_plots)
```

@@

```{r}
bootstrapped_fitted_all <- left_join(bootstrapped_fitted_all, country_map, on = "site_id")
count_icd_all <- left_join(count_icd_all, country_map, on = "site_id")
patient_count_psy_period_psy_all <- left_join(patient_count_psy_period_psy_all, country_map, on = "site_id")
patients_hospitalized_agg_sex_perc_all <- left_join(patients_hospitalized_agg_sex_perc_all, country_map, on = "site_id")
perc_disorder_group_all <- left_join(perc_disorder_group_all, country_map, on = "site_id")
ratios_patients_with_without_psy_all <- left_join(ratios_patients_with_without_psy_all, country_map, on = "site_id")

@@

```{r Extracting age information}
age_table1_all <- table1_all %>% 
  filter(name == "Age" | (name == "Total" & Category == "Sex")) %>% 
  select(name, siteid, before_pandemic, during_pandemic) %>% 
  pivot_longer(cols = c(before_pandemic, during_pandemic), 
               names_to = "period",
               values_to = "values") %>% 
  pivot_wider(names_from = name, 
              values_from = values, 
              id_cols = c(siteid, period)) %>% 
  mutate(mean_age = as.numeric(sub("\\s\\(.*", "", x = Age, perl = TRUE)),
         sd_age = as.numeric(str_extract(pattern = "(?<=\\(sd:\\s)[0-9]{1,2}\\.[0-9]{1,2}(?=\\))", 
                                         string = Age)), 
         Total = as.numeric(sub("\\s\\(.*", "", x = Total, perl = TRUE))
  ) %>% 
  group_by(period) %>% 
  summarise(conf_interval = gmodels::ci( mean_age ),
            mean_age = round(sum(Total * mean_age) / sum(Total), 2), 
            sd_age = round(sum(Total * sd_age) / sum(Total), 2), 
            ci_age = paste0("[", round(as.numeric(conf_interval[2]), 2), " , ",  round(as.numeric(conf_interval[3]),2), "]")) %>% 
  mutate(Age = paste0(as.character(mean_age), " (sd: ", as.character(sd_age), ")", as.character(ci_age))) %>% 
  select(period, Age) %>% 
  unique() %>%
  pivot_wider(names_from = period, values_from = Age) %>% 
  mutate(Category = "Age", 
         name = "mean (sd), 95% CI") %>% 
  select(Category, name, before_pandemic, during_pandemic) %>% 
  rename(before_pandemic_count = before_pandemic, 
         during_pandemic_count = during_pandemic)
```

@@

```{r}
# Recovering
coefficient_slope_calculation <- function(df, ...) {
  ts_linear_percent <- lm(percentage ~ period * time, df)
  linear_model <- broom::tidy(ts_linear_percent) %>%
    filter(term %in% c("periodduring_pandemic:time"))
}

coefficients_df <- patient_count_psy_period_psy_all %>% 
  group_by(siteid) %>% 
  group_modify(coefficient_slope_calculation) %>% 
  rename(observed_diff = estimate)
```

@@

```{r}
# Call function from another file : bootstrap.R
bootstrap_size <- 10000
binom_proportion <- function(n, prob, size) {
  (rbinom(n, size, prob) / size) * 100
}

@@

@@

bootstrapped_coefficients_all <- lapply(bootstrapped, `[[`, 1) %>% bind_rows()
bootstrapped_fitted_all <- lapply(bootstrapped, `[[`, 2) %>% bind_rows()
```

@@

```{r}
bootstrap_pvalue_calculation <- function(df, ...) {
  z <- unique(df[["observed_diff"]]) / sd(df[["periodduring_pandemic:time"]])
  pvalue_coeff_interaction <- round(pnorm(abs(z), lower.tail = FALSE) * 2, 3)
  pvalue_coeff_interaction <- ifelse( pvalue_coeff_interaction >= 0.01, round( pvalue_coeff_interaction, 2), pvalue_coeff_interaction)
  list("pvalue" = pvalue_coeff_interaction, 
       "observed_diff" = round(unique(df[["observed_diff"]]), 2)
  ) 
}

@@

```{r}
quantile_bootstrapped_fitted_all <- bootstrapped_fitted_all %>%
  group_by(time_p, period, siteid) %>%
  summarise("2.5%" = quantile(predicted, 0.025),
            "50%" = median(predicted, 0.5),
            "97.5%" = quantile(predicted, 0.975)) %>%
  pivot_longer(cols = c("2.5%", "50%", "97.5%"),
               names_to = "quantiles")
```

```{r}
df_coefficients_boot <- bootstrapped_coefficients_all %>% 
  left_join(coefficients_df, by = "siteid") 
names_site_id <- unique(df_coefficients_boot$siteid)

plot_annotations <- df_coefficients_boot %>% 
  group_by(siteid) %>% 
  group_map( bootstrap_pvalue_calculation ) %>% 
  set_names(names_site_id) %>% 
  lapply(FUN = function(vec) {
    paste0("Coeffs differences: ",
           vec$observed_diff,
           " (pvalue: ",
           format.pval(vec$pvalue,
                       digits = 2,
                       eps = 10**-5, 
                       nsmall = 2),
           ")")
  }) %>% 
  unlist()

### change p-value round

plot_annotations_df <- data.frame(
  siteid = names(plot_annotations), 
  label = plot_annotations
)
```

```{r}
bootstrapped_fitted_all <- bootstrapped_fitted_all %>% left_join(country_map, by = "siteid")

quantile_bootstrapped_fitted_all <- quantile_bootstrapped_fitted_all %>% left_join(country_map, by = "siteid")
```

```{r}
plot_annotations_df <-plot_annotations_df %>%
  left_join( country_map )

ggplot(bootstrapped_fitted_all, aes(x = time_p, y = predicted, group = interaction(iteration, period))) +
  facet_wrap("plotsLabel", scales = "free_y", labeller = label_wrap_gen(width = 35,multi_line = TRUE)) +
  geom_line(aes(color = period),
            alpha = 0.03) +
  geom_line(data = quantile_bootstrapped_fitted_all,
            aes(y = value, group = interaction(quantiles, period)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_all[quantile_bootstrapped_fitted_all$quantiles == "50%", ],
            aes(y = value, group = period)) +
  geom_point(data = patient_count_psy_period_psy_all,
             aes(y = percentage, group=NULL),
             alpha = 0.5) +
  scale_colour_manual(values = cbPalette) +
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  geom_label(data = plot_annotations_df, 
             aes(label=label), 
            x = -Inf,
            y = +Inf,
            hjust = 0,
            vjust = 1,
            size = 4,
            inherit.aes = FALSE) +
  labs(
    #title = "Interrupted Time Series Analysis: Percentage of patients with psychiatric conditions",
    #subtitle = "Parametric bootstrap estimation: (10000 iterations)",
       x = "Calendar dates",
       y = "Percentage",
       color = "Period") +
  theme(strip.text = element_text(size = 14),
        axis.text.x=element_text(angle = 45, hjust=1, size = 8),
        axis.text.y = element_text(size = 8), 
        axis.title.x = element_text(size = 8),
        axis.title.y = element_text(size = 8),
        title = element_text(size = 14),
        plot.subtitle = element_text(size = 12, face = "italic"), 
        legend.position="bottom") 
ggsave("figure1_boostrapped_all.png", height = 20, width = 45, units = "cm")
```

@@

```{r}
trends_siteid <- df_coefficients_boot %>% 
  group_by(siteid) %>% 
  summarise(mean_boot = mean(`periodduring_pandemic:time`),
            observed = unique(observed_diff),
            var_boot = var(`periodduring_pandemic:time`), 
            z = mean_boot / sqrt(var_boot), 
            pvalue = pnorm(z, lower.tail = FALSE)*2 )
```

@@

### By country
```{r}
m.country <- metagen(TE = pred,
                 seTE = sqrt( se**2 ),
                 data = trends_country,
                 studlab = country,
                 sm = "MN",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "DL")

@@

```{r Interrupted time series by sex}
patients_hospitalized_agg_sex_total <- patients_hospitalized_agg_sex_total %>% 
  mutate(period = ifelse(time_p <= as.Date("2020-03-15"), "before_pandemic", "during_pandemic")) %>% 
  select(time_p, period, sex, count_sex, percentage, siteid)
# %>% 
#   inner_join(country_map)
```

```{r }
bootstrapped_sex <- patients_hospitalized_agg_sex_total %>%
  group_by(sex) %>% 
  # group_by(plotsLabel, sex) %>% 
  mutate(month_year = format(time_p, "%m"),
         time = seq_along(time_p))  %>% 
 group_map(~ bootstrapping_slopes(.x,
                                  group_name = .y,
                                  bootstrap_size = bootstrap_size,
                                  count = "count_sex", 
                                  percentage = "percentage"))

bootstrapped_coefficients_sex <- lapply(bootstrapped_sex, `[[`, 1) %>% bind_rows()
bootstrapped_fitted_sex <- lapply(bootstrapped_sex, `[[`, 2) %>% bind_rows()
quantile_bootstrapped_fitted_sex <- bootstrapped_fitted_sex %>%
  # group_by(time_p, period, plotsLabel, sex) %>%
  group_by(time_p, period,  sex) %>%
  summarise("2.5%" = quantile(predicted, 0.025),
            "50%" = median(predicted, 0.5),
            "97.5%" = quantile(predicted, 0.975)) %>%
  pivot_longer(cols = c("2.5%", "50%", "97.5%"),
               names_to = "quantiles")
coefficients_df_sex <- patients_hospitalized_agg_sex_total %>% 
  group_by(sex) %>% 
  # group_by(plotsLabel, sex) %>% 
    mutate(month_year = format(time_p, "%m"),
         time = seq_along(time_p))  %>% 
  group_modify(coefficient_slope_calculation) %>% 
  rename(observed_diff = estimate)

df_coefficients_boot_sex <- bootstrapped_coefficients_sex %>% 
  # left_join(coefficients_df_sex, by = c("plotsLabel", "sex"))
  left_join(coefficients_df_sex, by = c("sex"))
```

@@

```{r annotation boostrap disorders}
names_sex <- unique(df_coefficients_boot_sex$sex)

plot_annotations_sex <- df_coefficients_boot_sex %>% 
  group_by(sex) %>% 
  group_map( bootstrap_pvalue_calculation ) %>%
  set_names(names_sex) %>% 
  lapply(FUN = function(vec) {
    paste0("Coeffs differences: ",
           vec$observed_diff,
           " (pvalue: ",
           format.pval(vec$pvalue, 
                       eps = 10**-5),
           ")")
  }) %>% 
  unlist()
plot_annotations_sex_df <- data.frame(
  sex = names(plot_annotations_sex), 
  label = plot_annotations_sex
)
```

@@

#### Oiriginal plot

@@

pvalue_sex_slope_diff <- bootstrap_pvalue_calculation(  df_coefficients_boot_sex[df_coefficients_boot_sex$sex == "female", ]
)

plot_annotations_sex_df <- paste0("Female proportion period differences: ",
                                  pvalue_sex_slope_diff$observed_diff,
                                  " (pvalue: ",
                                  format.pval(pvalue_sex_slope_diff$pvalue, 
                                              eps = 10**-5),")") %>%
  data.frame(label = ., 
             plotsLabel = "Female")
```

@@

bootstrapped_coefficients_disorder <- lapply(bootstrapped_disorders, `[[`, 1) %>% bind_rows()
bootstrapped_fitted_disorder <- lapply(bootstrapped_disorders, `[[`, 2) %>% bind_rows()
quantile_bootstrapped_fitted_disorder <- bootstrapped_fitted_disorder %>%
  # group_by(time_p, period, plotsLabel, sex) %>%
  group_by(time_p, period,  disorder_group) %>%
  summarise("2.5%" = quantile(predicted, 0.025),
            "50%" = median(predicted, 0.5),
            "97.5%" = quantile(predicted, 0.975)) %>%
  pivot_longer(cols = c("2.5%", "50%", "97.5%"),
               names_to = "quantiles")
coefficients_df_disorder <- perc_disorder_group_total %>% 
  group_by(disorder_group) %>% 
  mutate(month_year = format(time_p, "%m"),
         time = seq_along(time_p))  %>% 
  group_modify(coefficient_slope_calculation) %>% 
  rename(observed_diff = estimate)

@@

plot_annotations_disorder <- df_coefficients_boot_disorder %>% 
  group_by(disorder_group) %>% 
  group_map( bootstrap_pvalue_calculation ) %>%
  set_names(names_disorder) %>% 
  lapply(FUN = function(vec) {
    paste0("Coeffs differences: ",
           vec$observed_diff,
           " (pvalue: ",
           format.pval(vec$pvalue, 
                       eps = 10**-5),
           ")")
  }) %>% 
  unlist()
plot_annotations_disorder_df <- data.frame(
  disorder_group = names(plot_annotations_disorder), 
  label = plot_annotations_disorder
)
```

@@

### Disorder group 
```{r}
perc_disorder_group_total %>%
  ggplot( aes( x= as.Date( time_p ), y = percentage, group = disorder_group )) +
  facet_wrap( ~ disorder_group, scales = "free" ) +
  geom_line( aes(color = disorder_group )) +
  geom_point( aes( color = disorder_group )) +
  geom_vline(xintercept = as.Date(pandemic_start_date), linetype = "dashed")+
  labs(x ="", y = "percentage of patients (%)")+
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  theme(axis.text.x=element_text(angle = 45, hjust=1, size = 6),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA))

>>>>

Put all the aggregated counts from the different sites together
```{r}
for( i in 1:length( outputFiles )){
  print(outputFiles[i])
  load(paste0( outputDir, outputFiles[i]))
  if( i == 1 ){
    count_icd_all <- count_icd
    patients_hospitalized_agg_sex_perc_all <- patients_hospitalized_agg_sex_perc
    patient_count_psy_period_psy_all <- patient_count_psy_period_psy
    perc_disorder_group_all <- perc_disorder_group
    ratios_patients_with_without_psy_all <- ratios_patients_with_without_psy
    length_hospitalisation_values_all <- length_hospitalisation_values
    mental_codes_qc_output_all <- mental_codes_qc_output %>%
      select( disorder_group, description, concept_code, distinct_patients, distinct_observations, siteid )
    table1_all <- table1
  } else {
    count_icd_all <- rbind(count_icd_all, count_icd)
    perc_disorder_group_all <- rbind(perc_disorder_group_all, perc_disorder_group)
    patients_hospitalized_agg_sex_perc_all <- rbind( patients_hospitalized_agg_sex_perc_all, patients_hospitalized_agg_sex_perc)
    mental_codes_qc_output_all <- rbind( mental_codes_qc_output_all,
                                         mental_codes_qc_output %>%
                                           select( disorder_group, description, concept_code, distinct_patients, distinct_observations, siteid )
    )
    table1_all <- rbind( table1_all, table1)
    patient_count_psy_period_psy_all <- rbind( patient_count_psy_period_psy_all,patient_count_psy_period_psy)
    ratios_patients_with_without_psy_all <- rbind( ratios_patients_with_without_psy_all, ratios_patients_with_without_psy)
    length_hospitalisation_values_all <- tryCatch(
      rbind(length_hospitalisation_values_all, length_hospitalisation_values),
      error = function(e) length_hospitalisation_values_all
    )
    rm(count_icd,patients_hospitalized_agg_sex_perc,patient_count_psy_period_psy,
       perc_disorder_group,ratios_patients_with_without_psy,
       patient_count_psy_period_psy_clear, mental_codes_qc_output, table1, length_hospitalisation_values)
  }
}

@@

count_icd_all <- filter_by_dates(count_icd_all, start_date_plots, end_date_plots)
patient_count_psy_period_psy_all <- filter_by_dates(patient_count_psy_period_psy_all, start_date_plots, end_date_plots)
patients_hospitalized_agg_sex_perc_all <- filter_by_dates(patients_hospitalized_agg_sex_perc_all, start_date_plots, end_date_plots)
perc_disorder_group_all <- filter_by_dates(perc_disorder_group_all, start_date_plots, end_date_plots)
ratios_patients_with_without_psy_all <- filter_by_dates(ratios_patients_with_without_psy_all, start_date_plots, end_date_plots)
```

@@

```{r}
count_icd_all <- left_join(count_icd_all, country_map, on = "site_id")
patient_count_psy_period_psy_all <- left_join(patient_count_psy_period_psy_all, country_map, on = "site_id")
patients_hospitalized_agg_sex_perc_all <- left_join(patients_hospitalized_agg_sex_perc_all, country_map, on = "site_id")
perc_disorder_group_all <- left_join(perc_disorder_group_all, country_map, on = "site_id")
ratios_patients_with_without_psy_all <- left_join(ratios_patients_with_without_psy_all, country_map, on = "site_id")

@@

```{r Extracting age information}

age_table1_all <- table1_all %>% 
  filter(name == "Age" | (name == "Total" & Category == "Sex")) %>% 
  select(name, siteid, before_pandemic, during_pandemic) %>% 
  pivot_longer(cols = c(before_pandemic, during_pandemic), 
               names_to = "period",
               values_to = "values") %>% 
  pivot_wider(names_from = name, 
              values_from = values, 
              id_cols = c(siteid, period)) %>% 
  mutate(mean_age = as.numeric(sub("\\s\\(.*", "", x = Age, perl = TRUE)),
         sd_age = as.numeric(str_extract(pattern = "(?<=\\(sd:\\s)[0-9]{1,2}\\.[0-9]{1,2}(?=\\))", 
                                         string = Age)), 
         Total = as.numeric(sub("\\s\\(.*", "", x = Total, perl = TRUE))
  ) %>% 
  group_by(period) %>% 
  summarise(
    mean_age = round(sum(Total * mean_age) / sum(Total), 2), 
    mean_sd_age = round(sum(Total * sd_age) / sum(Total), 2), 
    ci_age = paste0(" [", round(mean_age - (qnorm(0.975) * mean_sd_age / sum(Total)), 5),
                    " , ",
                    round(mean_age + (qnorm(0.975) * mean_sd_age / sum(Total)), 5), "]")) %>% 
  mutate(Age = paste0(as.character(mean_age), " (sd: ", as.character(mean_sd_age), ")", as.character(ci_age))) %>% 
  select(period, Age) %>% 
  unique() %>%
  pivot_wider(names_from = period, values_from = Age) %>% 
  mutate(Category = "Age", 
         name = "mean (sd), 95% CI") %>% 
  select(Category, name, before_pandemic, during_pandemic) %>% 
  rename(before_pandemic_count = before_pandemic, 
         during_pandemic_count = during_pandemic)
```

@@

```{r}
# Estimating regression slopes from linear regression ('observed coefficients')
coefficient_slope_calculation <- function(df, slope_name = "periodduring_pandemic:time", ...) {
  ts_linear_percent <- lm(percentage ~ period * time, df)
  broom::tidy(ts_linear_percent) %>%
    filter(term %in% c(slope_name)) %>% 
    select(term, estimate)
}

coefficients_df <- patient_count_psy_period_psy_all %>% 
  group_by(siteid) %>% 
  group_modify(coefficient_slope_calculation,
               slope_name = c("time", "periodduring_pandemic:time")
               ) %>% 
  rename(observed_slope_coefficient = estimate)
```

@@

```{r}
# Call function from another file : bootstrap.R
bootstrap_size <- 100
binom_proportion <- function(n, prob, size) {
  (rbinom(n, size, prob) / size) * 100
}

@@

```{r}
bootstrap_pvalue_calculation <- function(df, slope_name, ...) {
  z <- unique(df[["observed_slope_coefficient"]]) / sd(df[[slope_name]])
  pvalue_coeff_interaction <- round(pnorm(abs(z), lower.tail = FALSE) * 2, 3)
  pvalue_coeff_interaction <- ifelse( pvalue_coeff_interaction >= 0.01, round( pvalue_coeff_interaction, 2), pvalue_coeff_interaction)
  list("pvalue" = pvalue_coeff_interaction,
       "observed_slope_coefficient" = round(unique(df[["observed_slope_coefficient"]]), 2)
  )
}
```

#### Calculate bootstrap

@@

bootstrapped_coefficients_all <- lapply(bootstrapped, `[[`, 1) %>% 
  bind_rows() %>% 
  rename(before_slope = time, 
         difference_slope = `periodduring_pandemic:time`) %>% 
  mutate(during_slope = before_slope + difference_slope) %>% 
  select(iteration, siteid, everything())

bootstrapped_fitted_all <- lapply(bootstrapped, `[[`, 2) %>% 
  bind_rows() %>%
  left_join(country_map, by = "siteid")

quantile_bootstrapped_fitted_all <- bootstrapped_fitted_all %>%
  group_by(time_p, period, siteid) %>%
  summarise("2.5%" = quantile(predicted, 0.025),
            "50%" = median(predicted, 0.5),
            "97.5%" = quantile(predicted, 0.975)) %>%
  pivot_longer(cols = c("2.5%", "50%", "97.5%"),
               names_to = "quantiles") %>% 
  left_join(country_map, by = "siteid")

@@

```{r}
df_coefficients_boot_primary <- bootstrapped_coefficients_all %>% 
  left_join(filter(coefficients_df, term == "periodduring_pandemic:time"),
            by = "siteid")

names_site_id <- unique(df_coefficients_boot_primary$siteid)

plot_annotations_primary <- df_coefficients_boot_primary %>% 
  group_by(siteid) %>% 
  group_map( bootstrap_pvalue_calculation, slope_name = "difference_slope" ) %>% 
  set_names(names_site_id) %>% 
  lapply(FUN = function(vec) {
    paste0("Coeffs differences: ",
           vec$observed_slope_coefficient,
           " (pvalue: ",
           format.pval(vec$pvalue,
                       digits = 2,
                       eps = 10**-3, 
                       nsmall = 2),
           ")")
  }) %>% 
  unlist()

plot_annotations_df_primary <- data.frame(
  siteid = names(plot_annotations_primary), 
  label = plot_annotations_primary
) %>%
  left_join( country_map ) 
```

```{r}
ggplot(bootstrapped_fitted_all,
       aes(x = time_p, y = predicted, group = interaction(iteration, period))) +
  facet_wrap("plotsLabel", scales = "free_y", labeller = label_wrap_gen(width = 35,multi_line = TRUE)) +
  geom_line(aes(color = period),
            alpha = 0.03) +
  geom_line(data = quantile_bootstrapped_fitted_all,
            aes(y = value, group = interaction(quantiles, period)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_all[quantile_bootstrapped_fitted_all$quantiles == "50%", ],
            aes(y = value, group = period)) +
  geom_point(data = patient_count_psy_period_psy_all,
             aes(y = percentage, group=NULL),
             alpha = 0.5) +
  scale_colour_manual(values = cbPalette) +
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  geom_label(data = plot_annotations_df_primary, 
             aes(label=label), 
            x = -Inf,
            y = +Inf,
            hjust = 0,
            vjust = 1,
            size = 4,
            inherit.aes = FALSE) +
  labs(
    #title = "Interrupted Time Series Analysis: Percentage of patients with psychiatric conditions",
    #subtitle = "Parametric bootstrap estimation: (10000 iterations)",
       x = "Calendar dates",
       y = "Percentage",
       color = "Period") +
  theme(strip.text = element_text(size = 14),
        axis.text.x=element_text(angle = 45, hjust=1, size = 8),
        axis.text.y = element_text(size = 8), 
        axis.title.x = element_text(size = 8),
        axis.title.y = element_text(size = 8),
        title = element_text(size = 14),
        plot.subtitle = element_text(size = 12, face = "italic"), 
        legend.position="bottom") 
ggsave("figure1_boostrapped_all.png", height = 20, width = 45, units = "cm")
```

## Secondary analysis : slopes before/during

```{r}
pvalues_boot_before <- bootstrapped_coefficients_all %>% 
  left_join(filter(coefficients_df, term == "time"), by = "siteid") %>% 
  group_by(siteid) %>% 
  group_map( bootstrap_pvalue_calculation, slope_name = "before_slope" ) %>% 
  setNames(unique(bootstrapped_coefficients_all$siteid)) %>% 
  bind_rows(.id = "siteid")

pvalues_boot_after <- bootstrapped_coefficients_all %>% 
  left_join(coefficients_df %>%
              pivot_wider(names_from = term,
                          values_from = observed_slope_coefficient) %>% 
              mutate(observed_slope_coefficient = time + `periodduring_pandemic:time`) %>% 
              select(siteid, observed_slope_coefficient),
            by = "siteid") %>% 
  group_by(siteid) %>% 
  group_map( bootstrap_pvalue_calculation, slope_name = "during_slope" ) %>% 
  setNames(unique(bootstrapped_coefficients_all$siteid)) %>% 
  bind_rows(.id = "siteid")

@@

@@

```{r}
trends_siteid <- df_coefficients_boot_primary %>% 
  group_by(siteid) %>% 
  summarise(mean_boot = mean(difference_slope),
            observed = unique(observed_slope_coefficient),
            var_boot = var(difference_slope), 
            z = mean_boot / sqrt(var_boot), 
            pvalue = pnorm(z, lower.tail = FALSE)*2 )
```

@@

### By country
```{r}
m.country <- metagen(TE = pred,
                 seTE = se,
                 data = trends_country,
                 studlab = country,
                 sm = "MN",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "DL")

@@

```{r}
patients_hospitalized_agg_sex_total <- patients_hospitalized_agg_sex_total %>% 
  mutate(period = ifelse(time_p <= as.Date("2020-03-15"), "before_pandemic", "during_pandemic")) %>% 
  select(time_p, period, sex, count_sex, percentage, siteid)
```

```{r }
bootstrapped_sex <- patients_hospitalized_agg_sex_total %>%
  group_by(sex) %>% 
  mutate(month_year = format(time_p, "%m"),
         time = seq_along(time_p))  %>% 
  group_map(~ bootstrapping_slopes(.x,
                                   group_name = .y,
                                   bootstrap_size = bootstrap_size,
                                   count = "count_sex", 
                                   percentage = "percentage"))

bootstrapped_coefficients_sex <- lapply(bootstrapped_sex, `[[`, 1) %>%
  bind_rows() %>% 
  rename(before_slope = time, 
         difference_slope = `periodduring_pandemic:time`)

bootstrapped_fitted_sex <- lapply(bootstrapped_sex, `[[`, 2) %>% bind_rows()

quantile_bootstrapped_fitted_sex <- bootstrapped_fitted_sex %>%
  group_by(time_p, period,  sex) %>%
  summarise("2.5%" = quantile(predicted, 0.025),
            "50%" = median(predicted, 0.5),
            "97.5%" = quantile(predicted, 0.975)) %>%
  pivot_longer(cols = c("2.5%", "50%", "97.5%"),
               names_to = "quantiles")

coefficients_df_sex <- patients_hospitalized_agg_sex_total %>% 
  group_by(sex) %>% 
  mutate(month_year = format(time_p, "%m"),
         time = seq_along(time_p))  %>% 
  group_modify(coefficient_slope_calculation, 
               slope_name = "periodduring_pandemic:time") %>% 
  rename(observed_slope_coefficient = estimate)

df_coefficients_boot_sex <- bootstrapped_coefficients_sex %>% 
  left_join(coefficients_df_sex, by = c("sex"))
```

@@

```{r }
names_sex <- unique(df_coefficients_boot_sex$sex)

plot_annotations_sex <- df_coefficients_boot_sex %>% 
  group_by(sex) %>% 
  group_map( bootstrap_pvalue_calculation, slope_name = "difference_slope" ) %>%
  set_names(names_sex) %>% 
  lapply(FUN = function(vec) {
    paste0("Coeffs differences: ",
           vec$observed_slope_coefficient,
           " (pvalue: ",
           format.pval(vec$pvalue, 
                       eps = 10**-3),
           ")")
  }) %>% 
  unlist()
plot_annotations_sex_df <- data.frame(
  sex = names(plot_annotations_sex), 
  label = plot_annotations_sex
)
```

@@

#### Original plot

@@

pvalue_sex_slope_diff <- bootstrap_pvalue_calculation(
  df_coefficients_boot_sex[df_coefficients_boot_sex$sex == "female", ], 
  slope_name = "difference_slope"
)

plot_annotations_sex_df <- paste0("Female proportion period differences: ",
                                  pvalue_sex_slope_diff$difference_slope,
                                  " (pvalue: ",
                                  format.pval(pvalue_sex_slope_diff$pvalue,
                                              digits = 2,
                                              eps = 10**-3, 
                                              nsmall = 2),")") %>%
  data.frame(label = ., 
             plotsLabel = "Female")
```

@@

bootstrapped_coefficients_disorder <- lapply(bootstrapped_disorders, `[[`, 1) %>%
  bind_rows() %>% 
  rename(before_slope = time, 
         difference_slope = `periodduring_pandemic:time`)

bootstrapped_fitted_disorder <- lapply(bootstrapped_disorders, `[[`, 2) %>%
  bind_rows()

quantile_bootstrapped_fitted_disorder <- bootstrapped_fitted_disorder %>%
  # group_by(time_p, period, plotsLabel, sex) %>%
  group_by(time_p, period,  disorder_group) %>%
  summarise("2.5%" = quantile(predicted, 0.025),
            "50%" = median(predicted, 0.5),
            "97.5%" = quantile(predicted, 0.975)) %>%
  pivot_longer(cols = c("2.5%", "50%", "97.5%"),
               names_to = "quantiles")
coefficients_df_disorder <- perc_disorder_group_total %>% 
  group_by(disorder_group) %>% 
  mutate(month_year = format(time_p, "%m"),
         time = seq_along(time_p))  %>% 
  group_modify(coefficient_slope_calculation, 
               slope_name = "periodduring_pandemic:time"
               ) %>% 
  rename(observed_slope_coefficient = estimate)

@@

plot_annotations_disorder <- df_coefficients_boot_disorder %>% 
  group_by(disorder_group) %>% 
  group_map( bootstrap_pvalue_calculation, slope_name = "difference_slope" ) %>%
  set_names(names_disorder) %>% 
  lapply(FUN = function(vec) {
    paste0("Coeffs differences: ",
           vec$observed_slope_coefficient,
           " (pvalue: ",
           format.pval(vec$pvalue, 
                       eps = 10**-3),
           ")")
  }) %>% 
  unlist()
plot_annotations_disorder_df <- data.frame(
  disorder_group = names(plot_annotations_disorder), 
  label = plot_annotations_disorder
)
```

@@

```{r}
perc_disorder_group_total %>%
  ggplot( aes( x= as.Date( time_p ), y = percentage, group = disorder_group )) +
  facet_wrap( ~ disorder_group, scales = "free" ) +
  geom_line( aes(color = disorder_group )) +
  geom_point( aes( color = disorder_group )) +
  geom_vline(xintercept = as.Date(pandemic_start_date), linetype = "dashed")+
  labs(x ="", y = "percentage of patients (%)")+
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  theme(axis.text.x=element_text(angle = 45, hjust=1, size = 6),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA))
